Decomposition-based Job-shop Scheduling with Constrained Clustering

### 2021-10-11 Artificial Intelligence and Machine Learning/PADL_conference/Paper_draft_v1.tex
update the results section

\newcommand{\stest}{\textit{ST\_EST}}

@@

  \item[Starting Time (ST)] is a set of features representing the starting execution time of each operation by solving the problem using a heuristic. In our work, we consider EST (\stest), First-In-First-Out (ST\_FIFO), and Most Total Work Remaining (ST\_MTWR), see \cite{overview} for an overview.
  To compute the starting time, we use a simple greedy algorithm \cite{tassel2021reinforcement,el2020job}, that at each step selects a not scheduled operation according to the heuristics and schedules it to a machine. In the case of FIFO, the algorithm selects an operation that appeared first in the queue. Similarly, for MTWR ...

  \item[Waiting Time (WT)] is also a set of features, like ST, for which computation we used three different heuristics EST (WT\_EST), FIFO (WT\_FIFO), and MTWR (WT\_MTWR). Each feature in \textit{WT} set is the difference between the scheduled starting time of a particular operation and its earliest possible starting time. The latter is the maximum out of the end processing time of the operation's predecessor and the time at which the required machine became available.
\end{description}

@@

We use the benchmark instances presented in \cite{taillard1993benchmarks} as a dataset to work on. Many researchers have studied these instances and presented different approaches to solving them. We also developed different decomposition strategies to solve those. Therefore, it will be possible to measure the success/failure of our proposed model by comparing the results of the strategies developed in the past with those obtained from the proposed algorithm. There are 12 features, as we described in the previous section. In order to know which features have a significant effect on the results, we did some combinations of the features to perform the decomposition process clustering-based and then solved the problem using the Answer Set Programming model developed in \cite{el2020job} with a timeout of 10 minutes. The combinations of the selected features are listed as follows:

@@

\item \textbf{F1} \textrightarrow \textit{\{ ST\textunderscore FIFO, ST\textunderscore MTWR, ST\textunderscore EST \}}
\item \textbf{F2} \textrightarrow \textit{\{ ST\textunderscore FIFO, ST\textunderscore MTWR, ST\textunderscore EST, RPT \}} 
\item \textbf{F3} \textrightarrow \textit{\{ ST\textunderscore FIFO, ST\textunderscore MTWR, ST\textunderscore EST, EST \}} 
\item \textbf{F4} \textrightarrow \textit{\{ ST\textunderscore FIFO, ST\textunderscore MTWR, ST\textunderscore EST, ML \}} 
\item \textbf{F5} \textrightarrow \textit{\{ ST\textunderscore FIFO, ST\textunderscore MTWR, ST\textunderscore EST, RPT, EST \}}
\item \textbf{F6} \textrightarrow \textit{\{ ST\textunderscore FIFO, ST\textunderscore MTWR, ST\textunderscore EST, RPT, ML \}} 
\item \textbf{F7} \textrightarrow \textit{\{ ST\textunderscore FIFO, ST\textunderscore MTWR, ST\textunderscore EST, EST, ML \}} 
\item \textbf{F8} \textrightarrow \textit{\{ ST\textunderscore FIFO, ST\textunderscore MTWR, ST\textunderscore EST, WT\textunderscore FIFO, WT\textunderscore MTWR, WT\textunderscore EST \}} 
\item \textbf{F9} \textrightarrow \textit{\{ ST\textunderscore FIFO, ST\textunderscore MTWR, ST\textunderscore EST, WT\textunderscore FIFO, WT\textunderscore MTWR, WT\textunderscore EST, RPT \}} 
\item \textbf{F10} \textrightarrow \textit{\{ ST\textunderscore FIFO, ST\textunderscore MTWR, ST\textunderscore EST, WT\textunderscore FIFO, WT\textunderscore MTWR, WT\textunderscore EST, EST \}} 
\item \textbf{F11} \textrightarrow \textit{\{ ST\textunderscore FIFO, ST\textunderscore MTWR, ST\textunderscore EST, WT\textunderscore FIFO, WT\textunderscore MTWR, WT\textunderscore EST, ML \}}
\item \textbf{F12} \textrightarrow \textit{\{ ST\textunderscore FIFO, ST\textunderscore MTWR, ST\textunderscore EST, WT\textunderscore FIFO, WT\textunderscore MTWR, WT\textunderscore EST, RPT, EST \}}
\item \textbf{F13} \textrightarrow \textit{\{ ST\textunderscore FIFO, ST\textunderscore MTWR, ST\textunderscore EST, WT\textunderscore FIFO, WT\textunderscore MTWR, WT\textunderscore EST, RPT, ML \}}
\item \textbf{F14} \textrightarrow \textit{\{ ST\textunderscore FIFO, ST\textunderscore MTWR, ST\textunderscore EST, WT\textunderscore FIFO, WT\textunderscore MTWR, WT\textunderscore EST, EST, ML \}}
\item \textbf{F15} \textrightarrow \textit{\{ ST\textunderscore FIFO, ST\textunderscore MTWR, ST\textunderscore EST, WT\textunderscore FIFO, WT\textunderscore MTWR, WT\textunderscore EST, RPT, EST, ML \}}

@@

We neglected the rank of an operation and the time length of a job because they had negative impact results from the preliminary experiments. The following Table~\ref{tab4} shows the selected features and the performance of each combination for solving benchmark instances of 50 jobs and 15 machines \cite{taillard1993benchmarks}. The following table shows the results of our experiments. The first column represents the instances we tested, and the next four columns show the makespan values obtained by FIFO, MTWR, and (EST with single and multi-shot) heuristics. From the sixth column, we show the makespan values obtained by combining the features mentioned above. Our experiments found that the first five combinations do not provide good solutions compared to the other heuristics. However, features (\textbf{F6}, \textbf{F8}, \textbf{F11}, \textbf{F12}, and \textbf{F15}) have a good impact in the cost function in the most cases. Especially, combinations \textbf{F6} and \textbf{F15} provided good results. It means that the most important features extracted from the problem itself and have a positive impact on the performance are \textit{Remaining Processing Time, Machine Load and Earliest Starting Time}. Also, The information obtained from the solutions of the other heuristics like (\textit{Starting Time} and \textit{Waiting Time}) led us to get better decomposition for the problem at hand. More specifically, combining \textit{Remaining Processing Time} with \textit{Machine Load} provides a good decomposition with/without \textit{Waiting Time} attributes obtained by the other heuristics. In a few instances, our proposed method did not outperform other heuristics, and the average makespan of \textbf{F6} was better than the average makespan obtained by the other heuristics and close to the FIFO makespan. The following section illustrates the difference between our proposed algorithm and the methods implemented by other researchers.

@@

      \textbf{FIFO}        & 3549                           & 3339                           & 3160                           & 3218 & 3291                           & 3325                           & 3654                           & 3299 & 3344                           & 3129 & 3331 \\
      \textbf{MTWR}        & 3364                           & 3304                           & 3168                           & 3494 & 3237                           & 3287                           & 3633                           & 3591 & 3394                           & 3257 & 3373 \\

@@

      \textbf{F2}          & 3362                           & 3318                           & 3585                           & 3425 & 3441                           & 3380                           & 3573                           & 3412 & 3416                           & 3315 & 3423 \\

@@

      \textbf{F6}          & \textbf{3294} & 3275                           & 3250                           & 3265 & 3386                           & 3366                           & \textbf{3480} & 3324 & 3430                           & 3327 & 3340 \\

@@

      \textbf{F14}         & 3554                           & 3373                           & 3524                           & 3232 & 3385                           & 3483                           & 3573                           & 3365 & 3284                           & 3767 & 3454 \\

@@

>>>>

\newcommand{\stest}{\textit{ST\_EST}}
\newcommand{\stmtwr}{\textit{ST\_MTWR}}
\newcommand{\stfifo}{\textit{ST\_FIFO}}

\newcommand{\wtest}{\textit{WT\_EST}}
\newcommand{\wtmtwr}{\textit{WT\_MTWR}}
\newcommand{\wtfifo}{\textit{WT\_FIFO}}

@@

  \item[Starting Time (ST)] is a set of features representing the starting execution time of each operation by solving the problem using a heuristic. In our work, we consider EST (\stest), First-In-First-Out (\stfifo), and Most Total Work Remaining (\stmtwr), see \cite{jones1998survey} for an overview.
To compute the starting time, we use a simple greedy algorithm \cite{el2020job}, that at each step selects a not scheduled operation according to the heuristics and schedules it to a machine. In the case of FIFO, the algorithm selects an operation that appeared first in the queue. Similarly, for MTWR, the algorithm selects the operation that belongs to the job with the longest processing time needed to be processed.

  \item[Waiting Time (WT)] is also a set of features, like ST, for which computation we used three different heuristics EST (\wtest), FIFO (\wtfifo), and MTWR (\wtmtwr). Each feature in \textit{WT} set is the difference between the scheduled starting time of a particular operation and its earliest possible starting time. The latter is the maximum out of the end processing time of the operation's predecessor and the time at which the required machine became available.
\end{description}

@@

We use the benchmark instances presented in \cite{taillard1993benchmarks} as a dataset to work on. Many researchers have studied these instances and presented different approaches to solving them. We also developed different decomposition strategies to solve those. Therefore, it will be possible to measure the success/failure of our proposed model by comparing the results of the strategies developed in the past with those obtained from the proposed algorithm. There are 12 features, as we described in the previous section. In order to know which features have a significant effect on the results, we did some combinations of the features to perform the decomposition process clustering-based and then solved the problem using the Answer Set Programming model developed in \cite{el2020job} with a timeout of 10 minutes. We started with a simple combination that consists of $3$ features; \stfifo, \stmtwr, and \stest. At each step, we added another feature to get a new combination. The combinations of the selected features are listed as follows:

@@

\item \textbf{F1} \textrightarrow \textit{\{ \stfifo, \stmtwr, \stest \}}
\item \textbf{F2} \textrightarrow \textit{\{ \stfifo, \stmtwr, \stest, RPT \}}
\item \textbf{F3} \textrightarrow \textit{\{ \stfifo, \stmtwr, \stest, EST \}} 
\item \textbf{F4} \textrightarrow \textit{\{ \stfifo, \stmtwr, \stest, ML \}} 
\item \textbf{F5} \textrightarrow \textit{\{ \stfifo, \stmtwr, \stest, RPT, EST \}}
\item \textbf{F6} \textrightarrow \textit{\{ \stfifo, \stmtwr, \stest, RPT, ML \}} 
\item \textbf{F7} \textrightarrow \textit{\{ \stfifo, \stmtwr, \stest, EST, ML \}} 
\item \textbf{F8} \textrightarrow \textit{\{ \stfifo, \stmtwr, \stest, \wtfifo, \wtmtwr, \wtest \}} 
\item \textbf{F9} \textrightarrow \textit{\{ \stfifo, \stmtwr, \stest, \wtfifo, \wtmtwr, \wtest, RPT \}} 
\item \textbf{F10} \textrightarrow \textit{\{ \stfifo, \stmtwr, \stest, \wtfifo, \wtmtwr, \wtest, EST \}} 
\item \textbf{F11} \textrightarrow \textit{\{ \stfifo, \stmtwr, \stest, \wtfifo, \wtmtwr, \wtest, ML \}}
\item \textbf{F12} \textrightarrow \textit{\{ \stfifo, \stmtwr, \stest, \wtfifo, \wtmtwr, \wtest, RPT, EST \}}
\item \textbf{F13} \textrightarrow \textit{\{ \stfifo, \stmtwr, \stest, \wtfifo, \wtmtwr, \wtest, RPT, ML \}}
\item \textbf{F14} \textrightarrow \textit{\{ \stfifo, \stmtwr, \stest, \wtfifo, \wtmtwr, \wtest, EST, ML \}}
\item \textbf{F15} \textrightarrow \textit{\{ \stfifo, \stmtwr, \stest, \wtfifo, \wtmtwr, \wtest, RPT, EST, ML \}}

@@

We neglected the rank of an operation and the time length of a job because they had negative impact results from the preliminary experiments. The following Table~\ref{tab4} shows the selected features, and the performance of each combination for solving benchmark instances of 50 jobs and 15 machines \cite{taillard1993benchmarks}. The following table shows the results of our experiments. The first column shows the approaches used for solving the problem in the literature in addition to the combinations of features we presented previously. The next columns represent the instances of our benchmark set except for the last column, which shows the average of each approach through the whole benchmark set. The first $4$ rows in the table show the values of each makespan obtained by heuristics; FIFO, MTWR, and (EST with a single and multi-shot). We can say that FIFO and MTWR provided the best results compared to the other two heuristics. However for the features combinations, the combinations (\textbf{F6}, \textbf{F8}, \textbf{F11}, \textbf{F12}and \textbf{F15}) provided good results according to the cost function in the most cases especially with combinations (\textbf{F6} and \textbf{F15}). It means that the most important features extracted from the problem itself and have a positive impact on the performance are \textit{Remaining Processing Time, Machine Load and Earliest Starting Time}. Also, The information obtained from the solutions of the other heuristics like (\textit{Starting Time} and \textit{Waiting Time}) led us to get better decomposition for the problem at hand. More specifically, combining \textit{Remaining Processing Time} with \textit{Machine Load} provides a good decomposition with/without \textit{Waiting Time} attributes obtained by the other heuristics. In a few instances, our proposed method did not outperform other heuristics, however, in the last column, the best average makespan of the other approaches was $3331$ by FIFO, and the average makespan of our feature selection algorithm was $3256$. We can conclude that the feature selection algorithm outperformed other heuristics in the literature. The following section illustrates the difference between our proposed algorithm and the methods implemented by other researchers.

@@

      \textbf{FIFO}        & 3549                           & 3339                           & \textbf{3160}              & \textbf{3218} & 3291               & 3325                           & 3654                           & \textbf{3299} & \textbf{3344}                           & \textbf{3129} & \textbf{3331} \\
      \textbf{MTWR}        & \textbf{3364}           & \textbf{3304}              & 3168                           & 3494 & \textbf{3237}                           & \textbf{3287}               & \textbf{3633}              & 3591 & 3394                           & 3257 & 3373 \\

@@

      \textbf{F2}          & 3362                           & 3318                           & 3585                           & 3425 & 3441                           & 3380                           & 3573                           & 3412 & 3416                           & \textbf{3315} & 3423 \\

@@

      \textbf{F6}          & \textbf{3294} & 3275                           & 3250                           & 3265 & 3386                           & 3366                           & \textbf{3480} & \textbf{3324} & 3430                           & 3327 & \textbf{3340} \\

@@

      \textbf{F14}         & 3554                           & 3373                           & 3524                           & \textbf{3232} & 3385                           & 3483                           & 3573                           & 3365 & 3284                           & 3767 & 3454 \\

@@

      \textbf{Obtained} & 3294                           & 3184 & 3143                           & 3232 & 3218 & 3229                           & 3480 & 3324 & 3145                           & 3315 & \textbf{3256} \\
\hline
